Section_8_Team1_Lab2_Report

### 2021-08-03 reports/Draft_Report.Rmd
added OMVB draft language and GGally code.

```{r setup, message=FALSE}
install.packages("table1")

#we may not need all of these
library(tidyverse)
library(magrittr)
library(ggplot2)
library(patchwork)
library(sandwich)
library(lmtest)
library(dplyr)
library(table1)
theme_set(theme_minimal())
knitr::opts_chunk$set(echo = TRUE)

@@

To create our dataframe, we cleaned and filtered data from multiple sources of data and joined based on texas county name or code.

@@

# final_depRep_tab_df = dplyr::count(Q2_df, DemorRep, sort = TRUE)
# colnames(final_depRep_tab_df) <- c('Voter Party', 'Number of Samples')
# knitr::kable(final_depRep_tab_df, caption="Final Samples by Party", align = "c")
```

@@

@@

#### Variable 1
#### Variable 2

>>>>

```{r setup, message=FALSE}
install.packages("table1")
install.packages("GGally")

#we may not need all of these
library(tidyverse)
library(magrittr)
library(ggplot2)
library(patchwork)
library(sandwich)
library(lmtest)
library(dplyr)
library(table1)
library("GGally")

theme_set(theme_minimal())
knitr::opts_chunk$set(echo = TRUE)

@@

To create our dataframe, we cleaned and filtered data from multiple sources of data and joined based on Texas county name or code.

@@

# final_depRep_tab_df = dplyr::count(df, #df2, sort = TRUE)
# colnames(final_depRep_tab_df) <- c('County Type', 'Number of Samples')
# knitr::kable(final_depRep_tab_df, caption="Final Samples by County", align = "c")
```

@@

ggpairs(df, columns = 1:ncol(data), title = "EDA: Variable Correlation",  
  axisLabels = "show", columnLabels = colnames(data[, columns]))

@@

#### Variable 1

One example of an omitted variable that may cause bias in our model is that of vehicle ownership among the population. It can certainly be expected that individuals that own a vehicle would be able to more easily travel short or long distances more frequently with relative ease. If an individual owned a vehicle, this would influence our model by driving the bias further from zero. From the data available, there would no immediate proxy for this omitted variable.

#### Variable 2

Another example of an omitted variable that may also cause bias in our model is fuel prices. Whether this is jet fuel or gasoline, fluctuations in this commodity would certainly impact travel costs. If fuel prices increase, it is generally observed that costs for travel increase. The opposite is also generally true. In the instance of increased fuel prices, this would influence our model by driving the bias closer to zero as distance traveled would drop. Conversely, if fuel prices for the time period of the sample for the population were lower, the bias would would be farther from zero.
